The pollination trade-off

### 2018-12-09 paper/manuscript.Rmd
Small fixes to questions
Fix figure 2

* Polish discussion. 
* Spell-check everything & check that reference list is correct.
* I think its not supper clear in the manuscript what is meant by a plant strategy. Need to re-check in the next iteration.

@@

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs. facilitation at the community level**. (a) Some species experience more competition for pollination than others. Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities. Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome. The number of plants analysed for each species is shown within brackets next to the species name. (b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas. (c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed. However, in the majority of cases, the difference is not large enough to be statistically significant at the 0.05 level. In all plots, error bars correspond to ± the standard error (SE)."}
# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
left <- cowplot::plot_grid(
  fig_hetero_con,
  NULL,
  fig_con_con[[1]],
  fig_con_con[[2]],
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)
right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)
cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
# dev.off()
```

>>>>

* Polish discussion, will appreciate input here. 
* Polish supp. info.
* Spell-check everything & check that reference list is correct.
* I think its not supper clear in the manuscript what is meant by a plant strategy. Need to re-check in the next iteration.

@@

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs. facilitation at the community level**. (a) Some species experience more competition for pollination than others. Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities. Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome. The number of plants analysed for each species is shown within brackets next to the species name. (b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas. (c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed. However, in the majority of cases, the difference is not large enough to be statistically significant at the 0.05 level. In all plots, error bars correspond to ± the standard error (SE)."}
# fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
left <- cowplot::plot_grid(
  fig_hetero_con,
  NULL,
  fig_con_con[[1]],
  fig_con_con[[2]],
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)
right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)
cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
# dev.off()
```
